Decision analysis for Bergen

### 2017-05-15 code/BergenDecisions/BergenDamageData.Rmd
Updated code for Bergen case

library(actuar)
library(RgoogleMaps)
source("getDamageData.R")
source("fitBurrDist.R")
source("getDamageMult.R")
source("getHallegatteData.R")
source("getChangeSlopes.R")
source("getDamageTrajectories.R")
source("getDiscountRate.R")
source("getAdaptationCost.R")
source("getUncertaintyTrajectories.R")
source("plotFigure1.R")
source("plotFigure2.R")
source("plotFigure3.R")
source("plotFigure4.R")
source("plotFigure5a.R")
source("plotFigure5b.R")
```

Read in yearly damage data (in MNOK) from Rogaland and Hordaland 1980 to 2015.
```{r}
sf.damage <- getDamageData()
round(sf.damage, 3)
```

Fit Burr distribution to damage data.   
```{r warning=FALSE}
par.est <- fitBurrDist(sf.damage)
round(par.est, 3)
```

Plot histogram of damage data and estimated Burr distribution. 
```{r}
plotFigure1(sf.damage, par.est, ifPdf=FALSE)
```

Get normalized data from Hallegatte et al. (2013) on relation between change in damage cost and sea level.  
```{r}
E <- getHallegatteData()
E
```
Extrapolate to any sea level rise. 
```{r}
slopes <- getChangeSlopes(E)
slopes
```

Plot changes in damages as a function of sea level rise with data from Hallegatte et al. (2013) indicated by black circles and the median change indicated with a red line. 
```{r}
plotFigure2(E, ifPdf=FALSE)
```

@@

Create damage distributions for 2016-2100 under various scenarios. 
```{r}
## res <- getDamageTrajectories(E, slopes, adaptation.cost) 
## save(res, file="data/calculatedDamage.RData")
load("data/calculatedDamage.RData")
```

Create plot that compares accumulated damage costs under various scenarios: Median projected cumulative damage costs under constant sea level (gray line), under sea level rise according to RCP 8.5 with no adaptation (black line) and with adaptation finished in 2047 (red line). The shaded area denotes the 90% projection interval under constant sea level.  Dotted lines indicate 90% projection intervals with sea level rise according to RCP 8.5.   
```{r}
plotFigure3(res, ifPdf=FALSE) 
```

Plot comparing total damage cost 2016-2100 under different adaptation timings, showing median total costs (red lines) and 90% projection intervals. Median projected total damage under no adaptation is indicated with a black line and the associated 90% projection interval with black dotted lines. 
```{r}
plotFigure4(res, ifPdf=FALSE) 
```

Investigation of the effects of uncertainty (no adaptation).
```{r}
res.unc <- getUncertaintyTrajectories(E=E, slopes=slopes, orig.damage=res$orig, damage.scenario=res$scenario)
total.damage <- apply(res$yearly, 1, sum)
summary(total.damage)
```

Plot comparing distributions of total damage for various uncertainty settings.
```{r}
plotFigure5b(res.unc, total.damage, ifPdf=FALSE)
```

>>>>

library(actuar)
library(RgoogleMaps)
source("getDamageData.R")
source("fitBurrDist.R")
source("getDamageMult.R")
source("getHallegatteData.R")
source("getChangeSlopes.R")
source("getDamageTrajectories.R")
source("getDiscountRate.R")
source("getAdaptationCost.R")
source("getUncertaintyTrajectories.R")
source("plotFigure1.R")
source("plotFigure2.R")
source("plotFigure3.R")
source("plotFigure4.R")
source("plotFigure5.R")
```

Read in yearly damage data (in MNOK) from Rogaland and Hordaland 1980 to 2015.
```{r}
sf.damage <- getDamageData()
round(sf.damage, 3)
```
Get normalized data from Hallegatte et al. (2013) on relation between change in damage cost and sea level.  
```{r}
E <- getHallegatteData()
E
```
Extrapolate to any sea level rise. 
```{r}
slopes <- getChangeSlopes(E)
slopes
```
Plot changes in damages as a function of sea level rise with data from Hallegatte et al. (2013) indicated by black circles and the median change indicated with a red line. 
```{r}
plotFigure2(E, ifPdf=FALSE)
```

Fit Burr distribution to damage data.   
```{r warning=FALSE}
par.est.res <- fitBurrDist(sf.damage, E)   
par.est <- par.est.res$par ## parameter estimates
round(par.est, 3)
mult <- par.est.res$mult ## multiplicative damage data corrections
round(mult, 3)
```

Plot histogram of damage data and estimated Burr distribution. 
```{r}
plotFigure1(sf.damage/mult, par.est, ifPdf=FALSE)
```

@@

Create damage distributions for 2016-2100 under various scenarios. 
```{r}
## res26 <- getDamageTrajectories(E, par.est, slopes, adaptation.cost, inputfile="data/Simulation_2_6.Rdata") 
## save(res26, file="data/calculatedDamage_nonstat26.RData")
## res45 <- getDamageTrajectories(E, par.est, slopes, adaptation.cost, inputfile="data/Simulation_4_5.Rdata") 
## save(res45, file="data/calculatedDamage_nonstat45.RData")
## res <- getDamageTrajectories(E, par.est, slopes, adaptation.cost, inputfile="data/Simulation_8_5.Rdata") 
## save(res, file="data/calculatedDamage_nonstat.RData")
load("data/calculatedDamage_nonstat.RData")
load("data/calculatedDamage_nonstat26.RData")
load("data/calculatedDamage_nonstat45.RData")
```

Create plot that compares accumulated damage costs under various scenarios: Median projected cumulative damage costs under constant sea level (blue line), under sea level rise according to RCP 8.5 with no adaptation (black line) and with adaptation finished in 2047 (red line). The blue shaded area denotes the 90% projection interval under constant sea level.  Dotted lines indicate 90% projection intervals with sea level rise according to RCP 8.5.   
```{r}
plotFigure3(res, ifPdf=FALSE) 
```

Plot comparing total damage cost 2016-2100 under different adaptation timings, showing median total costs (blue lines) and 90% projection intervals. Median projected total damage under no adaptation is indicated with a black line and the associated 90% projection interval with black dotted lines. 
```{r}
plotFigure4(res, ifPdf=FALSE) 
```

Investigation of the effects of uncertainty (no adaptation).
```{r}
res.unc <- getUncertaintyTrajectories(E=E,
                                      slopes=slopes,
                                      orig.damage=res$orig,
                                      damage.scenario=res$scenario,
                                      inputfile="data/Simulation_8_5.Rdata")
total.damage <- apply(res$yearly, 1, sum)
summary(total.damage)
res.unc26 <- getUncertaintyTrajectories(E=E,
                                        slopes=slopes,
                                        orig.damage=res26$orig,
                                        damage.scenario=res26$scenario,
                                        inputfile="data/Simulation_2_6.Rdata")
total.damage26 <- apply(res26$yearly, 1, sum)
summary(total.damage26)
res.unc45 <- getUncertaintyTrajectories(E=E,
                                        slopes=slopes,
                                        orig.damage=res45$orig,
                                        damage.scenario=res45$scenario,
                                        inputfile="data/Simulation_4_5.Rdata")
total.damage45 <- apply(res45$yearly, 1, sum)
summary(total.damage45)
```

Plot comparing distributions of total damage for various uncertainty settings.
```{r}
plotFigure5(res.unc, total.damage, res.unc45, total.damage45, res.unc26, total.damage26, ifPdf=FALSE, fileName="figures/UncertaintyLog.pdf")
```
